Comparing Power Optimizations in the Reorder Buffer

### 2011-06-07 paper/paper.tex
Adding bits to the paper.  Just pushing for shits.

\begin{document}
%TODO
\title{Compareing Power Optimizations in the Reorder Buffer}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Chen Guo\\
       \affaddr{UCLA Computer Science Department}\\
       \affaddr{4732 Boelter Hall}\\
       \affaddr{Los Angeles, CA 90095}\\
% 2nd. author
\alignauthor
Alex Edwards\\
       \affaddr{UCLA Computer Science Department}\\
       \affaddr{4732 Boelter Hall}\\
       \affaddr{Los Angeles, CA 90095}\\
% 3rd. author
\alignauthor
Henry Hsieh\\
       \affaddr{UCLA Computer Science Department}\\
       \affaddr{4732 Boelter Hall}\\
       \affaddr{Los Angeles, CA 90095}\\
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}
BLAH BLAH BLAH INTRO WEEEE
\section{TITLE1}
hi
\subsection{subsection title}
sub section.. with table!
\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

>>>>

\begin{document}
%TODO
\title{Comparing Power Optimizations in the Reorder Buffer}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Chen Guo\\
       \affaddr{UCLA Computer Science Department}\\
       \affaddr{4732 Boelter Hall}\\
       \affaddr{Los Angeles, CA 90095}\\
% 2nd. author
\alignauthor
Alexander Edwards\\
       \affaddr{UCLA Computer Science Department}\\
       \affaddr{4732 Boelter Hall}\\
       \affaddr{Los Angeles, CA 90095}\\
% 3rd. author
\alignauthor
Henry Hsieh\\
       \affaddr{UCLA Computer Science Department}\\
       \affaddr{4732 Boelter Hall}\\
       \affaddr{Los Angeles, CA 90095}\\
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}
BLAH BLAH BLAH INTRO WEEEE
\section{Project Implementation}
Our simulator provides a cycle accurate behavioral model of a standard circular re-order buffer.  At the outset of the project, the standard re-order buffer we intended to implement was a non-circular RAM-based re-order buffer.  However, after feedback from the course instructor and students it was decided that a circular buffer is more widely held as being the 'standard' buffer type and would serve as an ideal underlying model for power optimizations.  Thus, we implement and compare the standard circular re-order buffer to circular re-order buffers with the following optimizations: 1) Distributed (Cluster based) ROB, 2) Dynamically Sized ROB, 3) Reduced Output Port ROB (Retention Latch). The following sections outline each of the above model implementations as well as input instruction generation and power results tabulation.  
\subsection{Instruction Generation}
\subsection{Model Implementation}
\subsubsection{Circular ROB}
\subsubsection{Distributed ROB}
\subsubsection{Dynamic ROB}
\subsubsection{Reduced Output Port ROB (Retention Latch)}
\subsection{Power Tabulation Implementation}
\section{Results}
hi
\subsection{subsection titl}
sub section.. with table!
\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!
